### 2017-05-13 paper/intro.tex
pass on intro (discussing tradeoffs)

The dimensions of analysis we considered in this study are (i)
potential, (iii) adoption, (iv) speedup, and (iii) issues.  The
dimension \emph{feasibility} measures the potential of parallelization
to reduce testing costs.  In the limit, parallelization would be
fruitless if all projects used short-running test suites or if the
execution cost was dominated by a single test case in the suite.  The
dimension \emph{adoption} evaluates how often existing open-source
projects use parallelization schemes and how developers involved in
costly projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance of practitioners to
the technology and to understand their reasons.  The dimension
\emph{speedups} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  Finally, the dimension
\emph{issues} considers the problems in running tests in parallel
(\eg{}, test flakiness~\cite{luo-etal-fse2014}).  We briefly summarize
our findings in the following.

@@

\vspace{1ex}\noindent\emph{Speedups.}~We used two setups to measure
execution speedups.  In one setup we measured the speedups obtained on
projects that we knew a priori ran their test suite in parallel by
default.  In the other setup, we evaluated how execution scales with
the number of available cores in the machine.\Comment{We did not
  change parallel configurations on that setup.  For comparison, we
  disabled parallel execution to obtain the running time of a
  sequential execution.}  Considering the first setup, results
indicate that the average speedup of parallelization was
\avgSpeedup{}x.  Although we found cases with very high speedups (9.2x
for project Jcabi), we found cases where speedups were not very
significant.  Considering the scalability experiment, we noticed,
perhaps as expected, that speedups are bounded by long-running test
classes.

@@

\vspace{1ex}\noindent\emph{Issues.}~
\Fix{bla bla bla bla bla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla blabla bla bla
  blabla bla bla blabla bla bla blabla bla bla blabla bla bla blabla
  bla bla blabla bla bla blabla bla bla blabla bla bla bla}

>>>>

The dimensions of analysis we considered in this study are (i)
potential, (iii) adoption, (iv) speedup, and (iii) tradeoffs.  The
dimension \emph{feasibility} measures the potential of parallelization
to reduce testing costs.  In the limit, parallelization would be
fruitless if all projects used short-running test suites or if the
execution cost was dominated by a single test case in the suite.  The
dimension \emph{adoption} evaluates how often existing open-source
projects use parallelization schemes and how developers involved in
costly projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance of practitioners to
the technology and to understand their reasons.  The dimension
\emph{speedups} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  Finally, the dimension
\emph{tradeoffs} considers the problems in running tests in parallel,
including test flakiness~\cite{luo-etal-fse2014}.  We briefly
summarize our findings in the following.

@@

\vspace{1ex}\noindent\emph{Speedups.}~We used two setups to measure
execution speedups.  In one setup we measured the speedups obtained on
projects that we knew a priori ran their test suites in parallel by
default.  In the other setup, we evaluated how execution scales with
the number of available cores in the machine.\Comment{We did not
  change parallel configurations on that setup.  For comparison, we
  disabled parallel execution to obtain the running time of a
  sequential execution.}  Considering the first setup, results
indicate that the average speedup of parallelization was
\avgSpeedup{}x.  Although we found cases with very high speedups
(\eg{}, 9.2x for project Jcabi), we found cases where speedups were
not very significant.  Considering the scalability experiment, we
noticed, perhaps as expected, that speedups are bounded by
long-running test classes.

@@

\vspace{1ex}\noindent\emph{Tradeoffs.}~Test flakiness is a central
issue that can arise when running tests in parallel.  Dependent tests
can be affected by different schedulings of test methods and classes.
This dimension of the study measures the impact of different parallel
configurations on test flakiness and speedup.  Overall, results
indicate that parallel configurations that fork JVMs do not achieve
speedups as high as configurations that parallelize test classes and
methods, however they manifest much lower flakiness ratios.
